---
title: "Venudhar Ravishankar Homework 3"
output:
  html_document:
    self_contained: true
---

3.8.1

1. It's difficult to see how many points are in each area due to overplotting. We can fix this using jitter.

2. The amount, factor, and x parameters control this.

3. They're both point geoms, but jitter displaces each point randomly to illustrate the number of points in a region, but count enlarges each point to show this.

4. Default position is dodge. 
```{r}
library(ggplot2)

ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot()
```


3.9.1

2. It allows the user to change the labels of a plot.

4. It tells me that hwy is consistently higher than cty, but positively correlated. We need a 1:1 ratio so it's easier to observe this. geom_abline added the reference line (y=x) so that we could see that highway MPG is higher.


4.4

1. 'my_variable' is misspelled the second time, as 'my_varıable'.

2. Code below
```{r}
library(tidyverse)
library(ggplot2)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```

5.2.4

1. Code below
```{r}
library(nycflights13)

filter(flights, arr_delay >= 120)
filter(flights, dest %in% c('IAH', 'HOU'))
filter(flights, carrier %in% c('UA', 'AA', 'DL'))
filter(flights, month %in% c(7, 8, 9))
filter(flights, arr_delay >= 120 & dep_delay <= 0)
filter(flights, dep_delay >= 60 & (dep_delay - arr_delay >= 30))
filter(flights, 0 <= dep_time & dep_time <= 600)
```

2. Code below
```{r}
library(nycflights13)

filter(flights, between(dep_time, 0, 600))
```

3. Code below. 8255 rows have no dep_time. dep_delay, arr_time, arr_delay, tailnum (in some cases), and air_time are also missing. These rows appear to represent cancelled flights.
```{r}
library(nycflights13)

filter(flights, is.na(dep_time))
```

4. Any (nonzero) number raised to the power of zero evaluates to 1. Any boolean combined with `| TRUE` will return a value of TRUE. Any boolean combined with `& FALSE` will return a value of FALSE. If other information present is sufficient to determine the value of the expression, then R will evaluate the expression, replacing NA with any valid number. In the case of `NA \* 0`, however, since `Inf` is also a valid number and `Inf \* 0` evaluates to undefined (unlike any other number when multiplied by zero), R returns NA.

5.4.1

1. Listing them all sequentially; (contains('dep') | contains('arr')) -contains('sched'); dep_time:dep_delay -(sched_dep_time, sched_arr_time)

2. The second and all subsequent appearances of the column name are ignored.

3. one_of(c("items here")) allows one to select every item in the vector.

4. By default, matches for select helpers are case-insensitive. We can use `contains("TIME", ignore.case = FALSE)`.