---
title: "Venudhar Ravishankar Homework 2"
output:
  html_document:
    self_contained: true
---

3.2.4

1. I don't see anything, because the mapping was not specified

2. There are 234 rows and 11 columns

3. drv indicates the drive train. f = front-wheel drive, r = rear wheel drive, 4 = 4wd

5. We don't know how many dots there are in each class/drivetrain combination. All we know is presence or absence of at least one car.
```{r}
library(ggplot2)

ggplot(data = mpg) 
mpg 
?mpg 

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = class))
```

3.3.1

1. Color is a parameter of geom_point, and not of aes. It should be outside the aes call. Specifying it the way it's specified would only state which field should determine the color of each dot.

2. Categorical: manufacturer, model, trans, drv, fl, class. Continuous: displ, year, cyl, cty, hwy. I can see this based on the type of each variable; if it's an int or a chr, then it will be categorical. Else, it will be continuous.

3. A continuous variable cannot be mapped to shape. And the colors seem more natural in color mapping for continuous variables.

4. I still see the same data points, but just the behavior is different in different plots.

5. It modifies the width of the border. It works with mappings such as shape.

6. In this case, it colors points based on whether the condition is met (i.e. whether the displ is below 5 or not).

```{r}
library(ggplot2)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = displ))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = displ))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = drv)) #Cannot map a continuous variable to shape

?geom_point

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))
```

3.5.1

4. Since there are several classes, it is easier to see the separation between classes using faceting than it is using the color aesthetic. A disadvantage is that the ticks are only visible on the edges, so for subplots farther away from the edges, it would be more difficult for the viewer to know the number corresponding to any tick. If we had a larger dataset, then the smaller subplots would make it more difficult to see where each data point lies.

5. nrow and ncol specify the number of rows in which to organize the resulting subplots, respectively. as.table, dir, and shrink also are some options that control the layout.

```{r}
library(ggplot2)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)

?facet_wrap
?facet_grid
```

3.6.1

1. line geom; boxplot geom; bar geom; point geom

2. Code below

3. It hides the legend. It was used most likely because the colors made it clear enough what point belonged to what class.

4. It specifies whether to display the confidence interval or not.

5. They do not look different because the parameters that are shared between the smooth and point geoms are specified in the arguments to ggplot itself in the first example, but individually in the second.

6. Code below in the second snippet.
```{r}
library(ggplot2)

ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)

?geom_smooth

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

```

Code for #6 in 3.6.1
```{r}

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(se = FALSE)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, group=drv), se = FALSE)

ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color=drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color=drv)) + 
  geom_smooth(mapping = aes(x = displ, y = hwy), se = FALSE)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x=displ, y=hwy, color=drv)) + 
  geom_smooth(mapping = aes(x=displ, y=hwy, linetype=drv), se=FALSE)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x=displ, y=hwy, color=drv))

?aes_colour_fill_alpha
```

3.7.1

2. geom_bar makes the height of the bar proportional to the number of cases in each group, but geom_col uses stat_identity: it leaves the data as is.
```{r}
?geom_col
```


Extra question:
I believe that too many of the same colors were used throughout the document, but I like the choice of pie chart for "demand for data scientists" versus bar chart for "best source of new data talent". I wonder why a bar chart wasn't used in the next place as well.