---
title: "venudhar_ravishankar_midterm"
output: 
  html_document:
    toc: true
    toc_depth: 2
---

## Tidyverse Packages

### 1
Plotting: ggplot2
Data wrangling: dplyr

### 2
geom_point, filter, mutate, 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tibble)
```


## R Basics

### 1
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
```

### 2
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
```

### 3
They were all converted to strings, since at least one of them was a string.

## Data import/export

### 1
```{r}
rt <- read.delim("C:\\Users\\Venudhar\\Documents\\Berkeley X415.2\\compscix-415-2-assignments-master\\rail_trail.txt", sep="|")
```

### 2
```{r}
saveRDS(rt, file = 'rail_trail.rds')
rail_trail_rds <- readRDS('rail_trail.rds')

```

## Visualization

### 1
- We don't know how many respondents fit in each category (age, gender, etc.)

- The percentages in each row don't add up to 100; I'm assuming those people don't know the answer

- The circle sizes aren't useful since the numbers are what they represent

### 2
```{r}
```

### 3
We can change the above plot by using jitter, in the style of `position_jitter`.

## Data munging and wrangling

### 1
Every row should have a fields for country, population_1999, cases_1999, population_2000, and cases_2000. Each country would have a single row. 
```
group_by(table2, country) %>% summarise(
  population_1999 = sum(count[type = 'population', year = 1999]),
  population_2000 = sum(count[type = 'population', year = 2000]), 
  cases_1999 = sum(count[type = 'population', year = 1999]),
  cases_2000 = sum(count[type = 'population', year = 2000]))
```

### 2
```{r}
mutate(diamonds, price_per_carat = price / carat)
```

### 3
```
diamonds %>% group_by(cut) %>% summarise(
  count_diamonds_lowcarat_highprice = n([price > 10000 & carat < 1.5]),
  frac_diamonds_lowcarat_highprice = n([price > 10000 & carat < 1.5]) / n()
)
```

The results show that as cut quality increases, the price increases relative to weight. We should be concerned about color though.

## EDA

### 1
It's from 2000 to 2015.

### 2
46 cities

### 3
Houston in July 2015 with 8945 sales.
```{r}
txhousing %>% group_by(city, month, year) %>% summarize(numsales = sum(sales)) %>% arrange(-numsales)
```

### 4
I had guessed that more listings leads to more sales. Here is a query that groups by listings and aggregates the sum of sales.
```{r}
txhousing %>% group_by(listings) %>% summarize(numsales = sum(sales)) %>% arrange(listings)
```